\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.4em}
\setlist[enumerate]{leftmargin=1.4em}

\title{Void One\\Master Tape-Out Process Specification}
\author{VOID, Inc. -- Void One Directorate}
\date{Revision VOIDONE-2.0-FRONTIER-R1}

\begin{document}
\maketitle
\noindent\textbf{Design Version:} V2.0-FRONTIER-R1 \\
\textbf{Release ID:} VOIDONE-2.0-FRONTIER-R1 \\
\textbf{Program ID:} VOID-MASTER-TAPEOUT-ONE-2.0 \\
\textbf{Certification Target:} FRONTIER\_V2\_CERTIFIED \\
\textbf{Version Authority:} \texttt{VoidAlchmey/VERSION.json}

\tableofcontents
\newpage

\section{Purpose and Scope}
This document defines the binding fabrication specification for the Void One
program. It is written for foundry intake, mask preparation, process integration, packaging, and
post-fabrication validation teams.

This specification governs the Void compute lattice, topological control fabric, and economic-control
hardware pathways defined by:
\begin{itemize}
  \item \texttt{VoidAlchmey/src/sovereign\_core\_top.sv}
  \item \texttt{VoidAlchmey/src/harmonic\_oscillator.sv}
  \item \texttt{VoidAlchmey/src/topological\_braider.sv}
  \item \texttt{VoidAlchmey/src/subnet\_charter\_reg.sv}
  \item \texttt{VoidAlchmey/src/transaction\_routing\_alu.sv}
  \item \texttt{VoidAlchmey/src/string\_resonant\_alu.sv}
\end{itemize}

\section{Non-Negotiable Constitutional Constraints}
\subsection{No Silicon / No Copper Mandate}
The Void One is a post-silicon/post-copper architecture:
\begin{enumerate}
  \item No silicon substrate, no CMOS substitution, and no silicon photonic fallback are allowed.
  \item No copper vias, no copper interconnect closure, and no copper package reroute are allowed.
  \item Any tooling pass introducing silicon or copper content is non-compliant and requires immediate halt.
\end{enumerate}

\subsection{Zero Clock Mandate}
\begin{enumerate}
  \item Global clock trees are forbidden.
  \item PLL insertion, CTS synthesis, and synchronous clock-domain retrofit are forbidden.
  \item Event-driven resonant activation and local phase-coupled domains are mandatory.
\end{enumerate}

\subsection{Chakra + Cultivation Method Mandate}
The fabrication and mask translation flow shall preserve:
\begin{itemize}
  \item Chakra-band activation labels on routing domains and resonant compute regions.
  \item Cultivation-stage progression labels for all phase-coupled pathways.
  \item Coupled chakra/cultivation metadata in coordinate and GDS payloads.
\end{itemize}

\subsection{Golden-Ratio Curvilinear Geometry}
\begin{enumerate}
  \item Orthogonal-grid routing concepts are prohibited.
  \item 90-degree turns are prohibited.
  \item Preferred turning arcs shall use 137.507\degree progression.
  \item Width/length scaling shall follow \(\varphi = 1.6180339887\).
\end{enumerate}

\subsection{Dark-Channel Doctrine}
\begin{itemize}
  \item L4 shall preserve non-radiative transport assumptions (dark-channel transport).
  \item Photonic-first substitution is prohibited in the transport stack.
\end{itemize}

\subsection{L3 Layer-Locked Economic Control}
The \textbf{Recursive Treasury ALU is a physical, non-modifiable L3 Moir\'e feature}.
\begin{itemize}
  \item L3 material: Re6Se8Cl2 Moir\'e superatomic logic fabric.
  \item Treasury constants (618 bps inter-subnet, 16 bps intra-subnet) are hard-law controls.
  \item No ECO edits, post-mask patching, or firmware remap is allowed for L3 treasury pathways.
\end{itemize}

\section{Material Stack Definition (V2)}
\begin{longtable}{@{}lllll@{}}
\toprule
Layer & Material & Function & Thickness (\(\mu m\)) & Constraint \\
\midrule
\endhead
L0 & C60/Aerogel Composite & Surface-cool barrier + transient damping & 2.50 & Outer thermal safety envelope \\
L1 & 12C Isotopic Diamond & Thermal steering and containment & 50.00 & No silicon substitution \\
L2 & Beryllium Aluminate (BeAl2O4) & Mechanical/phase continuity & 1.50 & Preserve coupling continuity \\
L3 & Re6Se8Cl2 Moir\'e Logic & Topological compute + Recursive Treasury & 0.35 & \textbf{Non-modifiable} \\
L4 & Amorphous Carbon / BiSb & Dark-channel transport + shielding & 2.20 & Non-radiative doctrine required \\
L5 & Multi-doped Graphene & Coherent interconnect lattice & 0.12 & Copper prohibited \\
\bottomrule
\end{longtable}

\section{Thermodynamic Transmutation Doctrine}
The Void One uses bounded thermal bands:
\begin{itemize}
  \item \textbf{Cultivation Zone}: mild heat uplift improves lock quality and entropy harvest.
  \item \textbf{Sovereign Zone}: target sustained-throughput band.
  \item \textbf{Collapse Guard Zone}: automatic protection and route de-rating.
\end{itemize}
Thermal behavior beyond guard bounds is treated as protocol risk, not performance gain.

\section{Defect Sovereignty Protocol}
\begin{enumerate}
  \item Perform post-fabrication defect-map characterization.
  \item Export defect priors for runtime route arbitration.
  \item Preserve safety constraints while utilizing stable defect channels.
\end{enumerate}

\section{Hard-Law Economic and Routing Constraints}
For any transaction value \(V\):
\[
\mathrm{Tariff}_{inter} = \left\lfloor \frac{618}{10000}V \right\rfloor,\qquad
\mathrm{Lease}_{intra} = \left\lfloor \frac{16}{10000}V \right\rfloor
\]
\[
V_{routed} = V - \mathrm{Tariff}_{inter} - \mathrm{Lease}_{intra}
\]
Inter-subnet tariff paths must physically terminate in the immutable L3 treasury route.

\section{Verification and Sign-Off Gates}
Tape-out readiness requires all gates below to pass:
\begin{itemize}
  \item Formal proofs in \texttt{VoidAlchmey/validation/formal\_core.sby}.
  \item Thermal gradient + transmutation checks in \texttt{VoidAlchmey/validation/tcad\_isotopic\_diamond.py}.
  \item 950 K max-heat stress profile pass in \texttt{VoidAlchmey/validation/tcad\_report.json} (SovereignExcursion only).
  \item Dark-channel coherence checks in \texttt{VoidAlchmey/validation/void\_channel\_mesh.py}.
  \item Material compliance gate in \texttt{VoidAlchmey/validation/material\_compliance\_check.py}.
  \item Lattice generation from \texttt{VOID\_Sovereign\_Core\_Package/generate\_nanoscale\_lattice.py}.
  \item Foundry ALE calibration + metrology acceptance from \texttt{foundry\_modification\_protocol.md}.
\end{itemize}

\section{Foundry Prohibitions}
\begin{enumerate}
  \item Do not run clock-tree synthesis, skew balancing, or synchronous timing closure transforms.
  \item Do not introduce silicon/copper substitutions at any layer.
  \item Do not alter L3 Recursive Treasury geometry or hard-law constants.
  \item Do not flatten non-Abelian braid channels into commutative approximations.
  \item Do not reintroduce photonic-first assumptions into dark-channel layers.
\end{enumerate}

\section{Delivery Artifacts}
The package shall include:
\begin{itemize}
  \item \texttt{xenalchemy\_process\_spec.tex}
  \item \texttt{foundry\_intake\_letter.md}
  \item \texttt{foundry\_modification\_protocol.md}
  \item \texttt{generate\_nanoscale\_lattice.py}
  \item \texttt{nanoscale\_lattice.coords}
  \item \texttt{master\_tape\_out\_manifest.md}
\end{itemize}

\section{Acceptance Statement}
By accepting this specification, fabrication parties acknowledge that no-silicon/no-copper,
zero-clock, chakra/cultivation preservation, dark-channel doctrine, golden-ratio geometry,
non-Abelian topological protection, and L3 treasury immutability are mandatory engineering constraints.

\end{document}